Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory

### 2017-07-25 writing/supporting_information.tex
fix section position in SI
Minor change

xf% Created 2017-07-22 Sat 14:57
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=suppinfo,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
\date{}
\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\section{Figures}
\label{sec:orgf1e64ec}
\subsection{Dipole Orientation Profiles of MD Simulations}
\label{sec:org7a31239}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\linewidth]{../img/SI-dipole-profile.pdf}
\caption{\label{fig-SI-dipole}
Dipole orientation \(\cos \mu\) as a function of \(z\) in MD simulations of different systems (L, and GL with varied graphene doping densities). The orientation at the water-vacuum interface (\(z=20\) nm) is invariable in all cases, indicating a minimal effect of the long range Coulombic interaction on the selected interface.}
\end{figure}

@@

\subsection{Properties of First Water Layer Adjacent to Charged Graphene Surface}
\label{sec:orga56cc18}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{../img/SI_prop_1st_layer.pdf}
\caption{\label{fig-SI-1st}
Properties of the first water layer adjacent to the charged graphene surface. The following quantities are plotted as a function of \(\sigma_{\mathrm{2D}}\): (a) z-position of the first water layer with maximal value of \(\rho_{\mathrm{L}}\). (b) maximal \(\rho_{\mathrm{L}}\) of the first water layer. (c) z-position of the first water layer with maximal value of \(\delta_{\mathrm{L}}\). and (d) maximal \(\delta_{\mathrm{L}}\) of the first water layer.}
\end{figure}
\newpage{}

\subsection{Hydrogen Bond Profiles of MD Simulations}
\label{sec:orgd258855}

@@

\subsection{Explanation for Shift of \(\Delta \Phi_{\mathrm{Coul}}\) Maximum from Charge Neutral State}
\label{sec:orgf365dc0}

@@

\subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
\label{sec:org00f40dc}

>>>>

% Created 2017-07-24 Mon 21:42
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=suppinfo,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

\newpage{}
\section{Figures}
\label{sec:orgedeb1ea}
\subsection{Dipole Orientation Profiles of MD Simulations}
\label{sec:org0dfc0ff}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\linewidth]{../img/SI-dipole-profile.pdf}
\caption{\label{fig-SI-dipole}
Dipole orientation \(\cos \mu\) as a function of \(z\) in MD simulations of different systems (L, and GL with varied graphene doping densities). The orientation at the water-vacuum interface (\(z=20\) nm) is invariable in all cases, indicating a minimal effect of the long range Coulombic interaction on the selected interface.}
\end{figure}

@@

\subsection{Properties of First Water Layer Adjacent to Charged Graphene Surface}
\label{sec:org697bf5c}
\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{../img/SI_prop_1st_layer.pdf}
\caption{\label{fig-SI-1st}
Properties of the first water layer adjacent to the charged graphene surface. The following quantities are plotted as a function of \(\sigma_{\mathrm{2D}}\): (a) z-position of the first water layer with maximal value of \(\rho_{\mathrm{L}}\). (b) maximal \(\rho_{\mathrm{L}}\) of the first water layer. (c) z-position of the first water layer with maximal value of \(\delta_{\mathrm{L}}\). and (d) maximal \(\delta_{\mathrm{L}}\) of the first water layer.}
\end{figure}
\newpage{}

\subsection{Hydrogen Bond Profiles of MD Simulations}
\label{sec:orgd29efcb}

@@

\subsection{Explanation for Shift of \(\Delta \Phi_{\mathrm{Coul}}\) Maximum from Charge Neutral State}
\label{sec:orgdeeca1e}

@@

\clearpage{}

\subsection{Fitting of the \(\Delta \Phi\) - \(\sigma_{\mathrm{2D}}\) Data in MD Simulations}
\label{sec:org7e59573}
